Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-10 Docs/IJES/journal.tex
[A-14] In ESBMC-SS, how are the decision variables selected in each instance? Could a solution be evaluated several times in a same iteration or/and in different iterations?

\vspace{2 mm}
It is possible to instruct ESBMC with which type of values the variables must be tested. Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values. \textcolor{blue}{Those values are selected by the SMT Solver during its execution, which is responsible to test once all possible combinations in order to yield a feasible solution. If this is achieved, the ASSUME directive ensures the compliance of the constraint $A.x \leq b$}.

>>>>

\vspace{2 mm}
It is possible to instruct ESBMC with which type of values the variables must be tested. Therefore, there is a declaration to populate all decision variables $x$ with non-deterministic Boolean values. \textcolor{blue}{As a result, the Boolean value that is assigned to each decision variable $x_i$ is actually selected by the SMT Solver, during its solving phase, which checks once all possible combinations to yield a feasible solution, {\it e.g.}, by handling the terms in the given background theory using a decision procedure~\cite{DeMoura2008,Brummayer2009}. If this is achieved, the ASSUME directive ensures the compliance of the constraint $A.x \leq b$}.
